\thetitle

### 2023-06-03 lang-design.tex
Fix Grammar

We can support partial dependent eliminator as well, but partial dependent eliminator can deduce "prec" and our "prec" is enough to construct this left inverse for (non-indexed) inductive type. 
\begin{minted}{Coq}
  pdelim : ∀ (P : D → Set), .., 
  (rᵢ : (∀ (x : Aᵢ) (w : Bᵢ x → D), (∀ (b : Bᵢ x), option (P (w b))) 
    → option (P (dᵢ x w)))),  .., ∀ (d : D) → option (P d)
\end{minted}
To generalize to indexed inductive type, we need to base on indexed W type~\cite{martin1982constructive, morris2009indexed,jashug2017}. We have mechanized the argument for indexed W type and dependent eliminator, but for the case with only one constructor in "C" and "D". This mechanization\footnote{\url{https://gist.github.com/DKXXXL/9b4e48350b966fa3739cfb71f1a9a852}} is a direct generalization of the proof for \cref{thm:prec-complete}.

>>>>

We can support a partial dependent eliminator as well. Though the partial dependent eliminator can deduce "prec", our "prec" is enough to construct this left inverse for (non-indexed) inductive type. 
\begin{minted}{Coq}
  pdelim : ∀ (P : D → Set), .., 
  (rᵢ : (∀ (x : Aᵢ) (w : Bᵢ x → D), (∀ (b : Bᵢ x), option (P (w b))) 
    → option (P (dᵢ x w)))),  .., ∀ (d : D) → option (P d)
\end{minted}
To generalize to indexed inductive type, we need to base on indexed W type~\cite{martin1982constructive, morris2009indexed,jashug2017}. We have mechanized the argument for indexed W type and dependent eliminator, but for the case with only one constructor in "C" and "D". This mechanization\footnote{\url{https://gist.github.com/DKXXXL/9b4e48350b966fa3739cfb71f1a9a852}} is a direct generalization of the proof for \cref{thm:prec-complete}.
